\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{diagbox}
\usepackage{todonotes}

% Shifted into macros.tex
%\newcommand{\VTNote}[1]{\todo{VT: #1}}
%\newcommand{\prob}{\mathit{Pr}}
%\newcommand{\U}{\mathcal{U}}
\include{macros}

\begin{document}
	
	\title{Privacy of aggregated up- and down- votes for Right To Ask}

\section{Introduction}
This analysis is complementary to the analysis of \cite{kiayias2022privacy}, in that it looks at the privacy implications of revealing aggregated data, while that work examines sharing the trust assumptions around various participants so that the decryption capability is not held by a fixed set of parties.

We consider the privacy model appropriate for aggregated bits. In our setting, these bits are up-votes (1) and down-votes (0) in Right To Ask, which are homomorphically aggregated to produce totals without revealing any other information about individual votes.

Totals can of course reveal information, with certainty if they are unanimous and in a probabilistic way even if they are not. This report considers a series of increasingly complex models of vote privacy in this setting.

\subsection{What are we trying to achieve? Differences between a standard election privacy model and the privacy model of Right To Ask}

The privacy model for traditional first-past-the-post elections is simple: an election authority traditionally publishes exact aggregates, with coercion-resistance as a secondary goal. In principle, it might be possible to prove who won without revealing exact tallies; in practice as far as we know this is never done. In practice sometimes the level of aggregation is varied for privacy reasons (for example, sometimes aggregate tallies may not be revealed at the level of individual polling places or by method of voting, though often they are). The requirement for exact answers generally precludes differentially private solutions.

This means that there is some coercion risk, particularly to distinguished groups and particularly in the case of anonymity or near-anonymity. 

Right To Ask has a significantly different privacy model: there are many questions to be voted on, and people's contributions are probably highly correlated---they will tend to up-vote similar questions, and down-vote similar questions, if they see them. However, the system is less dependent on exact answers, and the consequences of individual privacy breach may be less serious, than in government elections.

In summary, the Right To Ask privacy model has the following characteristics. 
\begin{itemize}
	\item Each up- or down-vote is a public ciphertext. Thus the system reveals who responded to which questions.
	\item Aggregated tallies are revealed.
	\item Slight perturbations of aggregated tallies are acceptable.
	\item People respond to multiple questions, in a way that may be highly correlated.
\end{itemize}


\paragraph{Notation} Assume fixed batches of size $B$. A ballot can only ever appear in a single batch, and once counted will not be counted again as part of any future batch. 

Let $V = \{ v_1, v_2,\ldots,v_B\}$ be the set of votes.

\section{Attacks and defences}

\subsection{Balancing Votes}
There is likely to be more upvotes than downvotes because downvotes are only from explicit dismissals. There has been some discussion on increasing the votes from just Up and Down, to Up2, Up1, Down1, Down2. What they mean remains to be decided, but it could be as follows:
\begin{itemize}
\item Up2 - Upvote having read the contents of the question, i.e. some additional engagement has taken place - e.g. retweet on twitter
\item Up1 - Upvote from question alone, e.g. a like on twitter
\item Down1 - Scrolled past, no engagement
\item Down2 - Explicitly dismissed the question
\end{itemize}

Everything except Down1 requires an explicit user action. Down1 would be automatic, i.e., if you scroll past the question with no interaction an automatic Down1 vote is cast. The challenge with this is that the user may want to come back and upvote that question later, so how can we reverse the previous vote?

\subsection{Inverted Vote Submission}
If, when submitting a vote, the inverse of the vote is also submitted to the Bulletin Board it will be possible to invert a vote if someone changes their mind later. A submission therefore contains Vote and InverseVote. Only the vote is counted at this point. If a user subsequently replaces their vote, or changes it, then they just make a new submission, again with a Vote and InverseVote. The way this is tallied is that all VOtes and InverseVotes are tallied excluding the last InverseVote, effectively cancelling all previous vote in favour of the most recent. This would require a zero knowledge proof that the Vote and InverseVote sum to zero, but that should be fairly straightforward.

VT: Actually if we use the simplest possible EG implementation, with a single candidate 'up-vote' and a zero for a downvote, then your 'inverse vote' and EG's dummy are equivalent. There'd be a bit of fiddling to ensure that the tally verified. It's also not hard to generate the (multiplicative) inverse of an ElGamal encryption, so (depending on EG integration) it might be easier to do that on the fly than to get the client to upload matching pairs.

\subsection{Vote Sampling}
Instead of tallying all votes a random sample of the votes is taken and then the full result extrapolated from it. In this way, individual privacy is protected, assuming that there are at least 2 votes. To hide which votes were counted a vector of 1's or 0's would need to be constructed and mixed so as to hide, even from the server, which votes were included.

\subsection{Pagination Attack}
Dismissed questions are stored locally, not by the server, with the dismissals applied locally when viewing the file. This presents a synchronisation challenge, but also risks creating a timing based pagination attack in the future. Although how serious such an attack is remains to be seen.

Currently there is no pagination, the entire file of questions is downloaded, so there is no pagination attack. Although it is important that questions cannot contain external content, i.e. images or tracking pixels, otherwise the server or a third-party will be able to detect that a question has been shown. Again this is probably less of an issue in the App, unless remote content is loaded by labels/components automatically.

In time the file of questions will become too big and will require pagination. i.e. download the next 10 questions. The problem with this is that the timing between requests for paginated content could reveal information about whether a user has dismissed a question. At the extreme, if the user has dismissed all questions in the page then the next pagination request will occur almost immediately, instead of taking the appropriate amount of time to scroll through the page of questions.


\section{The super-simple solution with up- and down-votes}
Suppose we do the simplest possible thing: allow each participant to cast either an up- or a down-vote in response to each question.

\subsection{Downvotes as zero}
Suppose we have one candidate (in ElectionGuard) and that the vote is either 1 for that candidate, or zero in the case of a down-vote.

The votes would therefore look like:

\begin{tabular}{lrll}
	\\
	{\bf UI}  & {\bf value }&{\bf  vote} &{\bf  dummy }\\
	Down   & 0          & 0          & 1    \\
	Up   & +1          & 1          & 0    \\ \\
\end{tabular}

This takes two ciphertexts per vote: one for the contents and one for the EG dummy.
It is very efficient (in terms of ciphertext total) and very simple.

\subsection{Downvotes as a separate candidate}
A slightly more verbose alternative is to have two candidates: one for up and one for down.

\begin{tabular}{lrlll}
	\\
	{\bf UI}  & {\bf value }&{\bf  up-vote} &{\bf  down-vote} & {\bf  dummy }\\
	Down   & -1          & 0          & 1   & 0 \\
	Up   & +1          & 1          & 0    & 0\\ 
	Abstain/Zero & 0 & 0 & 0 & 1 \\
\end{tabular}
This uses 3 ciphertexts per vote.

This doesn't do anything for tally unanimity, but it does allow for an 'abstain' option which might have interesting privacy implications: it could either be added explicitly as a 'meh' option in the UI, or the app could add it automatically to some questions to hide which questions the participant had actually looked at.

More complicated variants on this theme are discussed in Section~\ref{sec:complexVoting}.

\section{Unanimous tallies}

\subsection{A very simple random model}
First assume that each vote is chosen randomly and independently, with a probability $p$ of being 1 (and $1-p$ of being 0). This is obviously an oversimplified model to try out some ideas and get some best-case results.
Let $\U$ be the event that all votes are unanimous, either all ones or all zeros.

$$
\begin{array}{rcl}
	\prob_{p,B}(\U) & = & p^{B} + (1-p)^B \\
\end{array}
$$

This is minimised at $1/2^{B-1}$ when $p=1/2$, but rises quickly for uneven bit distributions. Some example values for $B=20$ are shown below.

$$
\begin{array}{cccc}
p & 0.5 & 0.7 & 0.9 \\
\prob_{p,20}(\U) & 2 \times 10^{-6} & 8 \times 10^{-4} & 0.12
\end{array}
$$

If an attacker controls $\alpha$ fraction of participants, and hence knows their votes, then in an average batch in which $\alpha B$ votes are exposed, the probability of the rest being unanimous is

$$
\begin{array}{rcl}
\prob_{p,(1-\alpha)B}(\U) & = & p^{(1-\alpha)B} + (1-p)^(1-\alpha)B \\
\end{array}
$$

Some example values of $\prob_{p,\alpha \times 20}(\U)$ are shown below.


\begin{tabular}{lccc}
\backslashbox{$\alpha$}{$p$}  & 0.5 & 0.7 & 0.9 \\
%\alpha & & & & \\
0 & $2 \times 10^{-6}$ &$ 8 \times 10^{-4}$ & 0.12 \\
0.05 & $2 \times 10^{-6}$ & $1 \times 10^{-3}$& 0.13 \\
0.1  & $8 \times 10^{-6}$ & $2 \times 10^{-3}$ & 0.15 \\
0.2  & $3 \times 10^{-5}$ & $ 3 \times 10^{-3}$ & 0.18  \\
\end{tabular}

The probability of being in at least one unanimous set after participating in $c$ batches can be easily computed.

\subsection{Simple bit-adding mechanism} \label{sec:simpleAddBits}
Suppose we add $r$ random bits (independently and uniformly chosen) into each batch before aggregation, then subtract $r/2$ from the resulting tallies. This does not affect the average tally, but lowers the probability of unanimity.

$$
\prob_{p,B}(\U | \text{$r$ random extra bits}) = \prob_{p,B+r}(\U)
$$

In the next section we will discuss how to add encrypted randomness in a verifiably fair way.

\section{Differentially private aggregates}

\subsection{Definition}

From~\cite{dwork2014algorithmic}:

\begin{defn} 
A randomised algorithm $M$ with domain $\mathbb{N}^|X|$ is \emph{$(\epsilon,\delta)$-Differentially Private} 
if for all $S \subseteq \text{Range}(M)$ and for all $x,y \in \mathbb{N}^|X|$ such that $|| x-y||_1 \leq 1:$

$$ \prob (M(x) \in S) \leq \exp(\epsilon) \prob(M(y) \in S)+ \delta$$
\end{defn}

\subsection{Analysis of the simple bit-adding mechanism}
Consider the simple mechanism from Section~\ref{sec:simpleAddBits}.

\begin{prop}
The simple bit-adding mechanism is $(r, \log r)$ Differentially-Private.
\end{prop}
\begin{proof}
Let $x$ and $x'$ be adjacent databases with $B$ records (bits). Let $V$ ($0 \leq V \leq V$) be the number of up-votes (1s) in $x$---then $x'$ has $V-1$ or $V+1$.

Let $R$ be the random variable defined by the sum of $r$ bits added.

$M(x)$ outputs an apparent tally including the random padding. Some outputs in the range are not possible.

Case~1a: If $x'$ has $V+1$ 1s and $t \leq V-1$, then 
$$\prob(M(x) = t) = \prob(M(x')=t) = 0.$$


Case~2a: If $x'$ has $V+1$ 1s and $t = V$, then
$$\prob(M(x) = t) = \prob(R = 0) = 1 / 2^r$$ 
but
$$\prob(M(x') = t) = 0.$$ 

Case~3a: If $x'$ has $V+1$ 1s and $V+1 \leq t \leq V+r$, then 

$$\prob(M(x) = t) = \prob(R = t-V) = {r \choose {t-V}} / 2^r$$ 

$$
\begin{array}{rcl}
\prob(M(x') = t) & = & \prob(R = t-V-1) \\
				 & = & {r \choose {t-V-1}} / 2^r \\
				 & = & \frac{t-V}{r-t+V+1}     \prob(M(x) = t) \\
				 & \leq & r \prob(M(x) = t)  \text{       (max when $t=V+r$)}
\end{array}
$$

Case~4a: If $x'$ has $V+1$ 1s and $t = V+r+1$, then 
$$\prob(M(x) = t) = 0 $$
but
$$\prob(M(x') = t)  \prob(R = r) = 1 / 2^r.$$ 

Case~5a: If $x'$ has $V+1$ 1s and $t \geq V+r+2$, then 
$$\prob(M(x) = t) = \prob(M(x')=t) = 0.$$

So for Cases~1a--5a we have for all tallies $t$,

$$\prob(M(x') = t) \leq r \prob(M(x) = t) + 1/2^r$$  where the $1/2^r$ term comes from Case~4a.

Case~1b: If $x'$ has $V-1$ 1s and $t \leq V-2$, then 
$$\prob(M(x) = t) = \prob(M(x')=t) = 0.$$

Case~2b: If $x'$ has $V-1$ 1s and $t=V-1$, then this is similar to Case~2a.

Case~3b: If $x'$ has $V-1$ 1s and $V \leq t \leq V+r-1$, then this is similar to Case~3a

Case~4b: If $x'$ has $V-1$ 1s and $t = V+r$, then this is similar to Case~4a.
Case~5b: If $x'$ has $V-1$ 1s and $t \geq V+r+1$, then this is similar to Case~5a.

Therefore the mechanism is $(\log r, 1/2^r)$-Differentially Private.
\end{proof}

Since we are dealing with a simple counting query the sensitivity will always be 1. As such, we know what the laplace noise distribution will be in advance and don't need to perform a sensitivity analysis on the actual data.

\VTNote{Suggest writing this section to say more about what we're adding, which I agree is stock-standard DP. Then, in the next section, discuss how this can be added in a verifiably valid fashion. Occurs to me that the DP (or other) distribution may be completely independent of the actual distribution being added.}

\section{Verifiable Privacy Generation}

\paragraph{Pre-Generation of Noise}

One party in advanced generates a large amount of noise (for example, from the laplace distribution in the case of DP, or simply separate bits in the case of more simple padding) and commits, encrypts, and publishes the encryptions/commitments on the bulletin board. This could be a batch in the thousands, it depends how many counts are expected, but it can always be repeated to generate more noise.

Once committed to, a random percentage of the generated noise is revealed as an audit. That percentage will depend on what probability of detection of cheating wants to be achieved, however, it should a reasonably large number, maybe 50\%. The reason a large number is needed is that once all the data has been opened it should form a distribution closely approximate to the intended laplace distribution. If it does not then the whole batch is rejected. What counts as close will need some further thought and experimentation, if the number of values audited is large enough it should be very close to the intended laplace distribution.

The remaining unopened values should be mixed to prevent the generating party knowing the mapping between the final random values and the ones it generated. The mixed encrypted random values should be published on the bulletin board.

Note that this way the party who generated the values knows correlations between them, and that this could mean that tallies may leak information to that party even if they do not to the general public. (As an extreme example, if it happens that all the unopened values are zero then the fact they have been mixed is irrelevant.)

\paragraph{Adding Noise During the Count}

The votes are summed as normal and then an encrypted noise value is selected at random from the bulletin board and also added to the sum. The result is then decrypted and the answer should be a differentially private count of those votes.

Possible useful background on Verifiable DP: \cite{narayan2015verifiable,kato2021preventing}.

\paragraph{Perturbing existing votes probabilistically}

Suppose we can think of a way in which an existing El Gamal ciphertext can be perturbed (i.e. switched from 1 to 0 or vice versa) with some probability as part of a distributed process.

TODO think of a protocol.

\section{Changing the voting patterns}	 \label{sec:complexVoting}
An alternative is to leverage three or more different voting options. This doesn't remove the risk of unanimity, and doesn't solve the problem of revealing who voted on what questions, but it may make unanimity much less likely. (For example, Netflix has 'not for me' 'I like it' and 'love this!')

There are several ways this could work. For example, we could add an 'extra up-vote' option at the bottom of the QuestionDetailPage, and say it's worth +2. Similarly, we could add an explicit down-vote option there too, and call it 0 or -1.
Note that it doesn't really matter whether we call things -1, 0, +1 or 0,1,2 - we can just adjust the results afterwards. Worth thinking through some combinations.

Questions:
\begin{itemize}
	\item At the moment, we tally the total number of upvotes but don't subtract downvotes. Should we? Should we report the net upvote (up minus down) as a percentage? 
	\item What's the right relative importance of down/dismiss-voting, single-up-voting and double-up-voting? -1, +1, +2?
	\item Can we combine this with random padding to obscure who voted for what, at least somewhat?
\end{itemize}

** Question: How does EG currently handle range voting? Does it obscure how the tally was formed? That is, can we set multiple 'candidates' and sum all their tallies together without summing separate tallies?

\subsection{One candidate, two votes}
Suppose we have one candidate, and that each device can cast 2 votes (which is easy enough in EG because it's designed for settings where one pollsite computer casts multiple votes). In EG, we need a dummy that's always set up so that the sum of vote and dummy is the max value (in this case, 1).

The votes would therefore look like:

\begin{tabular}{lrll}
{\bf UI}  & {\bf value }&{\bf  vote} &{\bf  dummy }\\
Dismiss   & 0          & 0          & 1    \\
		  &            & 0          & 1    \\ 
		  & or  & & \\		  
		    &            & 0          & 1    \\ \hline
Up-vote   & +1          & 1          & 0    \\
		  &            & 0          & 1    \\   
		  & or  & & \\
		  &            & 1          & 0    \\
		  & or & & \\
		  &            & 0          & 1    \\   
		  &            & 1          & 0    \\  \hline
Double-up-vote & +2          & 1          & 0    \\
&            & 1          & 0    \\     
\end{tabular}

\paragraph{padding random values to obscure voting patterns}
Easy - can pad with a single-row Dissmis vote, and the voter can still come along later and add a single up-vote. It would mean that they couldn't come along later and double-up-vote.

The zero-pad would be indistinguishable from a single-up-vote, and the later addition of a (real) single-up-vote would be indistinguishable from double-up-voting something that had previously been single-up-voted. (This of course ignores timing issues, which might certainly allow an attacker to distinguish them.)

\paragraph{shifting the zero-point to interpret the output}
Zero, +1, +2 might not be the best interpretation of these user inputs. For example, we might prefer -1,0,+1. This scaling is easy: simply subtract 1 for each voter, regardless of whether they cast 1 or two votes. We could consider reporting both scaled and unscaled versions. For example, we could simply report total upvotes (without scaling) and then, separately, report the scaled total as a percentage.

However, -1,0,+1 might not be ideal---the zero-pad is actually the same as an up-vote, which is not great. See next section for how to fix this. 
 
\subsection{One candidate, three votes}
In this section we discuss how to spread the voting values out more, so as to allow for four distinct values for dismiss/down-vote, zero-pad, up-vote and double-up-vote. The idea is similar to the above, but allows each voter to cast 3 votes.
This time, it would only make sense to tally by subtracting 1 for each voter.

The idea is that each total could be produced by some combination of 1,2 or 3 ciphertexts, with only the double-up-vote actually requiring 3 ciphertexts. For the rest, the client would be free to choose a smaller number to cast sometimes, allowing for later additions (either to increase the upvote or to cast an initial +1 upvote on something already padded with zero).

The votes would look like:

\begin{tabular}{lrll}
	{\bf UI}  & {\bf value }&{\bf  vote} &{\bf  dummy }\\
	Dismiss   & 0          & 0          & 1    \\
  -1 after subtraction    	&       & 0          & 1    \\ 
	&            & 0          & 1    \\ 
	& or  & & \\		  
	&            & 0          & 1    \\ 
&            & 0          & 1    \\ 

	& or  & & \\		  
	&            & 0          & 1    \\ \hline
Zero-pad	 & +1          & 1          & 0    \\
0 after subtraction&           & 0          & 1    \\   
& or  & & \\
&            & 1          & 0    \\
& or & & \\
&            & 0          & 1    \\   
&            & 1          & 0    \\  
&            & 0          & 1    \\   
& etc. & & \\ \hline
	
	Up-vote   & +2          & 1          & 0    \\
+1 after subtraction	&            & 1          & 1    \\   
	& or  & & \\
	&            & 1          & 0    \\
	&            & 0          & 1    \\   
	&            & 1          & 0    \\  
	& etc. & & \\ \hline
	Double-up-vote & +2          & 1          & 0    \\
	&            & 1          & 0    \\     
		&            & 1          & 0    \\     \hline
\end{tabular}

The main problem with this is that you must cast at least two ciphertexts in order to up- or double-up-vote. A single zero-pad can subsequently be (singly) up-voted, but a zero-pad with two ciphertexts can't. This would mean that either we'd have to live with relatively frequent impossible-up-votes, or we'd have to use single-ciphertext zero pads most of the time, which would be easily distinguishable from up-votes.

\subsection{Up and Down candidates, with zero padding} \label{sec:upAndDown}
This takes 6 ciphertexts.

Suppose we have two candidates, Up and Down. Each person may vote once or twice. Each vote may contain 1 or 0 1's, so we need one padding ciphertext. The assumption is that our final tally is $T(\textit{Up}) - T(\textit{Down})$ where $T$ is EG's tallying function.

The votes would look like:

\begin{tabular}{lrlll}
	{\bf UI}  & {\bf value }&{\bf  Up}&{\bf  Down} &{\bf  dummy }\\
	Dismiss   & 1D          & 0          & 1    & 0\\
	& or  & & & \\		  
	&            & 0          & 1   & 0 \\ 
	&            & 0          & 0   & 1    \\ 
	& or  & & & \\		  
&            & 0          & 0   & 1    \\ 
&            & 0          & 1   & 0 \\  \hline
	Zero-pad	 & Net 0          & 0          & 0   & 1 \\
	& or  & & & \\
	&            & 1          & 0   & 0  \\
	&            & 0          & 1   & 0 \\   
	& or  & & & \\	
    &            & 0          & 1   & 0 \\
	&            & 1          & 0   & 0  \\ \hline
	
	Up-vote   & 1U          & 1          & 0   & 0 \\
	& or  & & & \\
	&            & 1          & 0  & 0  \\
	&            & 0          & 0 & 1    \\   
	& or  & & & \\
&            & 0          & 0 & 1    \\  
&            & 1          & 0  & 0  \\ \hline
	Double-up-vote & 2U          & 1          & 0  & 0  \\ 
	&            & 1          & 0  & 0  \\     \hline
\end{tabular}

\textit{**Question: Can we get EG to tally $T(\textit{Up} - \textit{Down})$ without computing the two tallies separately? This is certainly doable with standard crypto (just aggregate the Down candidate's votes by dividing rather than multiplying) but I'm not sure that EG supports it, or that it will pass standard verification. TODO: check.  We can perhaps ask them.}

If not, the main risk here is that it reveals unanimous non-existent downvotes if $T(\textit{Down}) = 0$. Perhaps we could include a 'neutral' option explicitly, i.e. a sort of manual version of the zero-pad?

Apart from that, it has a lot of good properties:
\begin{itemize}
	\item A (single) up-vote converted into 2U is indistinguishable from a (single) zero-pad converted into either an up-vote or a down-vote. (You still can't double-up-vote something that's been zero-padded, but that's not so bad.)
	\item A (double) up-vote is indistinguishable from a (double) dismiss, zero-pad, or double-up-vote.
\end{itemize}

\subsection{Extension of Section~\ref{sec:upAndDown} if EG doesn't allow summed columns}
This significantly ameliorates the risk of unanimous 0 for 'Down'. Only relevant if EG requires us to tally it separately.

Again, everyone gets two votes, each for two different candidates, Up and Down. However, the first vote is allowed up to 2 selections. This only affects Zero-pad (in a way that doesn't matter much) and single up-vote.

Up-vote can now be:

\begin{tabular}{lrllll}
	{\bf UI}  & {\bf value }&{\bf  Up}&{\bf  Down} &{\bf  dummy~1 } &{\bf  dummy~2 }\\
	
	Up-vote   & 1U          & 1          & 0   & 1 \\
	& or  & & & \\
	&            & 1          & 0  & 0 & 1 \\
	&            & 0          & 0 & 1  &   \\   
	& or  & & & \\
	&            & 0          & 0 & 1  & 1  \\  
	&            & 1          & 0  & 0 &  \\ 
		& or  & & & \\
	&            & 1          & 1 & 0  & 0  \\  
	&            & 1          & 0  & 0 &  \\
		& or  & & & \\
	&            & 1          & 0 & 1  & 0  \\  
	&            & 1          & 1  & 0 &  \\
\end{tabular}


Obviously the padding can be rearranged.

Now the important point is that some single up-votes will have a 1 in the Down column. Hence much less chance of unanimous zeros.

I'm not sure whether EG allows different maxima for votes on the same question. If not, we'd have to add a second dummy for the second vote too, hence 8 ciphertexts per vote.

\subsection{Privacy analysis of the different options}
Note that there are several different attackers with different knowledge and power:
\begin{itemize}
	\item an authority, who generates (some of) the randomness,
	\item a timing-based attacker, who sees what goes up on the BB in real time,
	\item an after-the-fact attacker, who only sees the final state of the BB.
\end{itemize}
\bibliographystyle{alpha}
\bibliography{bib}

\end{document}